New modal operators for constructive mathematics

### 2023-09-11 slides-herrsching2023.tex
What can constructive forcing do for you?

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{4.95cm}\includegraphics[width=\paperwidth]{topos-horses-lighter}\end{minipage}}
\begin{frame}{Constructive forcing}
  \medskip
  \begin{columns}[t]
    \begin{column}{0.40\textwidth}
      \quad\includegraphics[width=0.8\textwidth,valign=t]{branching}
    \end{column}

@@

>>>>

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{4.95cm}\includegraphics[width=\paperwidth]{topos-horses}\end{minipage}}
\begin{frame}{Constructive forcing}
  \medskip
  \begin{columns}[t]
    \begin{column}{0.40\textwidth}
      \quad\includegraphics[width=0.8\textwidth,valign=t]{branching}
    \end{column}

@@

\begin{frame}{What can forcing do for you?}
  \vspace*{-0.5em}

  \begin{columns}
    \begin{column}{0.45\textwidth}
      \begin{block}{1. Explore foundational possibility}
        There are forcing extensions with~\textsc{ch}, $\neg$\textsc{ch},
        \textsc{lem}, $\neg$\textsc{lem}, \ldots
      \end{block}
    \end{column}
    \pause

    \begin{column}{0.45\textwidth}
      \begin{block}{2. Demonstrate unprovability}
        The fundamental theorem of algebra is \hil{not constructively provable}
        as there is a forcing extension where \hil{it is false}.
      \end{block}
    \end{column}
  \end{columns}
  \pause
  \bigskip

  \begin{columns}
    \begin{column}{0.45\textwidth}
      \begin{block}{3. Harness convenient fictions}
        For every set, there is a forcing extension where it is
        \hil{countable}.
      \end{block}
    \end{column}
    \pause

    \begin{column}{0.45\textwidth}
      \begin{block}{4. Constructivize classical theories}
        A preorder~$X$ is well iff the \hil{generic sequence} $\NN \to X$ is
        good.
      \end{block}
    \end{column}
  \end{columns}
  \pause
  \bigskip

  \begin{columns}
    \begin{column}{0.45\textwidth}
      \begin{block}{5. Study parametric mathematics}
        Eigenvectors depend continuously on the parameter
        iff, in a suitable forcing extension, they merely exist.
      \end{block}
    \end{column}
    \pause

    \begin{column}{0.45\textwidth}
      \begin{block}{6. Build synthetic accounts}
        \emph{See lectures by Matthias Hutzler.}
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
